---
title: "Spatial Autocorrelation"
author: "Yi-Min Chang Chien"
date: "22/05/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## F-test

In general, an F-test in regression compares the fits of different linear models. Unlike t-tests that can assess only one regression coefficient at a time, the F-test can assess multiple coefficients simultaneously.

The F-test of the overall significance is a specific form of the F-test. It compares a model with no predictors to the model that you specify. A regression model that contains no predictors is also known as an intercept-only model.

The hypotheses for the F-test of the overall significance are as follows:

Null hypothesis: The fit of the intercept-only model and your model are equal.
Alternative hypothesis: The fit of the intercept-only model is significantly reduced compared to your model.

If the P value for the F-test of overall significance test is less than your significance level, you can reject the null-hypothesis and conclude that your model provides a better fit than the intercept-only model.


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## library calls
```{r}
library(rgdal)
library(rgeos)
library(tidyverse)
library(raster)
library(sf)
library(sp)
library(raster)
library(dplyr)
library(spdep)
library(GISTools)
library(tmap)
```


## Data Preparation

```{r}
##### 1. Data pre-processing for voxel viewshed analysis  
setwd("/Users/Yi-Min/R session/Lake District/")
dem <- readGDAL("DEM_25m")
class(dem)
plot(dem)
```

## LCM2015 

```{r}
# 2.2 pre-processing LCM2015 25m land cover for voxel viewshed analysis 
setwd("/Users/Yi-Min/R session/Lake District/CEH LCM2015/")
"lcm-LakeDist-25m" %>% readGDAL() -> lcm
class(lcm)
dim(dem) == dim(lcm)
plot(lcm)
```

